---
title: "Data Visualisation Workshop"
author: "Your name and U number"
date: "Today's date"
output:  
    html_document:
        toc: true
        toc_depth: 4
        theme: cosmo
        number_sections: false
        toc_float: true
        highlight: pygments
        fig_width: 8
        fig_height: 4
---

# **Task 1**: Loading the data
Load data
```{r}
library("tidyverse")

flowcell <- read_csv("raw_data/flowcell_A.csv")
flowcell_summary <- read_csv("raw_data/two_flowcell_channel_summary.csv")
```
use skimr to get overview 
flowcell is raw data from a single flowcell, flowcell A. Every row represents a single sequencing read
```{r}
library(skimr)

skim(flowcell)

```
channel has 512 variables which is correct 
time start in seconds is skewed to be shorter time 
length is also skewed to be shorter (which is not good because longer is better)
the mean of q score is 7.85, which means about half are considered good and half are considered bad (but more good)
the q score is also bimodal with two obvious peaks 
hour matches seconds which makes sense 


flowcell_summary summarises the total output for each of the 512 channels in two flowcells - flowcell A and flowcell B
```{r}
library(skimr)

skim(flowcell_summary)
```
it has 512 channels which is good
total number of bases sequenced is skewed so theres less bases 
row is uniformly distributed which is good because this shouldn't change 
column drops off at the end which makes sense as maybe all the collumns didnt fill up





# **Task 2**: Overview Plot

# **Task 3**: Comparing flowcells

# **Task 4**: Are the flowcells faulty?